\chapter{General remarks}
\label{ch:general_remarks}

%------------------------------------

\section{Notes on the assignment}
\label{sec:notes_on_ass}

None of the assignments for the Software Architectures course were submitted in the first examination period due to personal reasons.
Because of this, all of the code written for this assignment is written specifically for the second examination period.
All code was written by using the course material and the online Akka documentation\footnote{\url{https://doc.akka.io/docs/akka/2.5.32/}}.

%------------------------------------

\section{Important design assumptions}
\label{sec:design_assumptions}

Whilst the assignment gave great details on which components should be created, there were some gaps in connecting these components.
It was opted to create extra non-specified functionality of adding stock houses and products so that these gaps are filled realistically compared to hard-coding \texttt{ActorRef} lists and \texttt{ProductsWithQuantity} in stock.
Sadly, this decision left no time to implement extra patterns such as a persistent business handshake pattern.

%------------------------------------

\section{Important files}
\label{sec:important_files}

All code written is available on the GitHub repository for this assignment \citep{github_project}. 
Rights to this private GitHub repository can be granted upon request. 
A copy of this GitHub repository is accompanied by this report.
An overview of important files is given below:
\begin{itemize}
    \item \texttt{README.md}
    \begin{itemize}
        \item General information of the GitHub repository as well as some technical details about the used environment and how to run the project.
        \item A section called \texttt{Validated output} where the main functionality is discussed informally by discussing some screenshots.
    \end{itemize}
    \item \texttt{assignment.pdf}, \texttt{Lennert-Bontinck-SA3.pdf} and \texttt{report/}
    \begin{itemize}
        \item The assignment PDF, this report and the source files of the report. A VUB themed \LaTeX{} template by \citet{latex_template} was used to create this report.
    \end{itemize}
    \item \texttt{code/Lennert-Bontinck-SA3/}
    \begin{itemize}
        \item The folder containing the code of the assignment solution.
        \item Instructions on how to run the code are available in the \texttt{README.md} file.
    \end{itemize}
\end{itemize}